Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-05 docs/ms.tex
Update ms.tex

This paper is orgnized as following: In section 2 we introduce the
weak lensing formulas and the likelihood function .Then we describe
two flexible models for the intrinsic shape distribution. In section
3 we show the result of the MCMC sampling ,and check the bias and
variance of sample mean and compare with that of the simple average
method.In Section 4 we discussed

>>>>

This paper is orgnized as following: In section 2 we introduce the
weak lensing formulas and the likelihood function .Then we describe
two flexible models for the intrinsic shape distribution. In section
3 we show the result of the MCMC sampling ,and check the bias and
variance of sample mean and compare with that of the simple average
method.In Section 4 we discussed the systematical bias ,mean square error
and effects of prefactor $\xi$ and galaxy shape measurement error.
